Observed vs. Simulated Year Comparison

### 2023-03-13 03-post-process/output-plots-children/02-mcmc-diags.Rmd

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("Yr1 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
base = c("delta_O0_O1[pop]", "Lphi_O0_O1_resid[1,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

>>>>

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("Yr1 NOR:HOR Scaler", "Yr2 NOR:HOR Scaler", "Yr1 Initial Residual", "Yr 1 AR(1) Coefficient")
base = c("delta_O0_O1[pop]", "delta_O1_O2[pop]", "Lphi_O0_O1_resid[1,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

### 2023-03-13 03-post-process/output-plots-children/10-noise-term-diags.Rmd

  # calculate posterior summaries of standardized qresidual time series
  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))

@@

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "red")
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

@@

  # calculate posterior summaries of qresidual time series
  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))

  # place qresiduals at correct place in a time series
  # ie., insert missing values
  empty = matrix(NA, nrow = 5, ncol = length(obs_qresid_yrs))
  empty[,y_ind] = qresid
  qresid = empty[,observable]
  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%")
  empty_names = rep(NA, length(obs_qresid_yrs))
  empty_names[y_ind] = colnames(qresid_post)

>>>>

  # calculate posterior summaries of standardized qresidual time series
  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975, 0.25, 0.75))))

@@

  # draw the noise time series: mean and 95% CRI
  segments(all_yrs[observable], qresid["2.5%",], all_yrs[observable], qresid["97.5%",], col = "salmon")
  segments(all_yrs[observable], qresid["25%",], all_yrs[observable], qresid["75%",], col = "salmon", lwd = 4)
  points(qresid["mean",] ~ all_yrs[observable], pch = 21, col = "red", bg = "salmon", cex = 1.25)

@@

  # calculate posterior summaries of qresidual time series
  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975, 0.25, 0.75))))

  # place qresiduals at correct place in a time series
  # ie., insert missing values
  empty = matrix(NA, nrow = 7, ncol = length(obs_qresid_yrs))
  empty[,y_ind] = qresid
  qresid = empty[,observable]
  rownames(qresid) = c("mean", "sd", "50%", "2.5%", "97.5%", "25%", "75%")
  empty_names = rep(NA, length(obs_qresid_yrs))
  empty_names[y_ind] = colnames(qresid_post)
